% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\usepackage{enumitem}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{}

\begin{document}

\hypertarget{channels}{%
\section{Channels}\label{channels}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \texttt{location}: send the location. The \texttt{location} channel is
  the channel transfers the location data from the \texttt{CV} to the
  core. Then, the core will send the location data to the \texttt{RC}
  (Robot Controller) to make decisions based on the location data.
\end{enumerate}

\hypertarget{location-cv}{%
\subsection{\texorpdfstring{\texttt{location-cv}}{location-cv}}\label{location-cv}}

The \texttt{location-cv} channel is the channel that transfers the
location data from the \texttt{CV} to the core. It is normally a
3-element array, which contains the x, y coordinates and the angle of
the robot (yaw).

\hypertarget{location-rc}{%
\subsection{\texorpdfstring{\texttt{location-rc}}{location-rc}}\label{location-rc}}

The \texttt{location-rc} channel is the channel that transfers the
location data from the core to the \texttt{RC} (Robot Controller). It is
normally a 3-element array, which contains the x, y coordinates and the
angle of the robot (yaw).

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \texttt{block}: send colored block information. The \texttt{block}
  channel is the channel transfers the block information from the
  \texttt{CV} to the core. Then, the core will send the block
  information to the \texttt{RC} (Robot Controller) to make decisions
  based on the block information.
\end{enumerate}

\hypertarget{block-cv}{%
\subsection{\texorpdfstring{\texttt{block-cv}}{block-cv}}\label{block-cv}}

The \texttt{block-cv} channel is the channel that transfers the block
information from the \texttt{CV} to the core. It is normally a 3-element
array, which contains the x, y coordinates and the color of the block.

\hypertarget{block-rc}{%
\subsection{\texorpdfstring{\texttt{block-rc}}{block-rc}}\label{block-rc}}

The \texttt{block-rc} channel is the channel that transfers the block
information from the core to the \texttt{RC} (Robot Controller). It is
normally a 3-element array, which contains the x, y coordinates and the
color of the block.

\end{document}
